The evolution of gene expression in the term placenta of viviparous mammals

### 2016-02-18 manuscript/manuscript.Rnw
describe species abbreviation

\newcommand{\genetreeexplanation}[1]{Gene tree and heatmap of
  expression of genes related to #1. The gene tree was obtained from
  Ensembl~\cite{Cunningham.ea2015:Ensembl2015} and genes from species
  not included in this study or having expression by \ac{FPKM} less
  than 1 were excluded from the plotted tree. Heatmap cells in white
  are from species where there was no expression of the relevant
  transcript (or a species where that transcript does not apply).}

>>>>

\newcommand{\genetreeexplanation}[1]{Gene tree and heatmap of
  expression of genes related to #1. The gene tree was obtained from
  Ensembl~\cite{Cunningham.ea2015:Ensembl2015} and genes from species
  not included in this study or having expression by \ac{FPKM} less
  than 1 were excluded from the plotted tree. Heatmap cells in white
  are from species where there was no expression of the relevant
  transcript (or a species where that transcript does not apply). The
  species names are abbreviated with the first letter of the genus and
  first two letters of the species (for example, \textit{Homo sapiens}
  is \textit{H.sa.}). Genes with duplicate gene names in the same
  species (or no gene named defined) are listed by the Ensemble gene
  ID.}
